### 2014-03-12 Draft/abstract.tex
Changed to new ACM Format
+ added sig-alternate class for new ACM format
+ fixed abstract as per Dr. Xie's comments
+ added eval results Table in evaluation

\begin{abstract}
Temporal specifications of an Application Programming
Interface (API) describe allowed sequences of invocations
of methods within an API. Despite being desirable for 
software testing and verification (through formal analysis tools),
most API's do not have formal temporal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based automated approach \tool ,
to infer formal temporal specifications from natural language text of API documents.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of 70\% precision and 80\% recall
in inferring 63 temporal constraints from more than 2400 sentences of API documents.

>>>>

\begin{abstract}
Temporal specifications of an Application Programming
Interface (API) describe allowed sequence of invocations
of methods within an API. Despite being desirable for 
software testing and verification (through formal analysis tools),
most API's do not have formal temporal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
Although existing techniques infer from API documents method specifications (such as method precondition and postconditions) or resource specifications (such as constraints on creating/releasing resources), such techniques fail to explicitly infer temporal constraints.
Manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based automated approach \tool,
to infer formal temporal specifications from natural language text of API documents.
\tool\ uses 
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and \amazonAPI.
Our evaluation results show that \tool\ achieves an average of 66\% precision and 70\% recall
in inferring 69 temporal constraints from more than 3900 sentences of API documents.

### 2014-03-12 Draft/evaluation.tex
updated to ACM style
Changed to new ACM Format
+ added sig-alternate class for new ACM format
+ fixed abstract as per Dr. Xie's comments
+ added eval results Table in evaluation

$F-Score$ = $\frac{2 X Precison X Recall}{Precision + Recall}$

\end{center}

@@

@@

We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence.

We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence (producing false positives). For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. \tool\ fails to make the distinction

>>>>

$F-Score$ = $\frac{2 X Precison X Recall}{Precision + Recall}$
\end{center}

@@

\begin{table*}
\begin{center}

\caption{Evaluation Results}

\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline API & Methods & No. of Sentences & Spec Sentences & ICON Ann & TP & FP & FN & P & R & F-Score \\ 
\hline java.io &  & 2417 & 78 & 87 & 56 & 31 & 22 & 64.4 & 71.8 & 67.9 \\ 
\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 \\ 
\hline Total &  & 3909 & 90 & 99 & 64 & 35 & 26 & 64.6$^*$ & 71.1$^*$ & 67.7$^*$ \\ 
\hline
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{6.5in}}{\footnotesize $^*$ Column average; TP: Total number of True Positives; 
FP: Total number of False Positives; FN: Total number of False Negatives; P: Precision; R: Recall} \\ 
\end{tabular}
\end{center}
\end{table*}

@@

We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence. \textbf{A example goes here}

We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence (producing false positives). For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. \tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''. However \tool\ fails to make the distinction that it happens internally (enforced within the body) in the method. \tool, thus incorrectly identifies the sentence as a specification sentence.
